

 Before  I  can  open  my  gym  locker,  I  must  remember  the  combination.   Two  of  the numbers of this three-term sequence are 17 and 24, but I have forgotten the third, and donot know which is which.  There are 40 possibilities for the third number.  At ten secondsper try,  at most how long will it take me to test every possibility?  The answer is not 40minutes!
 
 %\--------------------------------
 
 

Kevin, Joseph, and Nicholas are 3 brothers. If the following statements are all true, which of them is the youngest?

    Kevin is the oldest.
    Nicholas is not the oldest.
    Joseph is not the youngest.

Merlin realizes that all Alakazams are Open Sesames, and some Hocus Pocuses are Alakazams.

Is it true that some Hocus Pocuses are Open Sesames?

Note: There is at least one of each item.

Kayle (yellow) Inara (blue)
One of the women above is named Kaylee and the other is named Inara. They each make a statement as shown; if we know that at least one of them is a lie, what is the color of the shirt that Inara is wearing?

5 brothers compare their heights and find that

    Alex is taller than Brian but shorter than Charlie;
    Daniel is taller than Edward but shorter than Alex.

Who is the tallest? Charlie

\textbf{Truth seeking puzzles}

1. There is exactly 1 false statement in this list.
2. There are exactly 2 false statements in this list.
3. There are exactly 3 false statements in this list.

3 cannot be true.
1 cannot be true

~\cite{clessa1996math}
Only one of these five statements is correct - which is it?
(1) Only one of these statements is false.
(2) Only two of these statements are false.
(3) Three of these statements are false.
(4) Four of these statements are false.
(5) All five of these statements are false.


~\cite{clessa1996math}
Some ducks are marching across a path. There's a duck in front
of two ducks, there's a duck behind two ducks, and there's a
duck in the middle of two ducks.
What's the least number of ducks that there could have been?

~\cite{clessa1996math}
Here's a simple multiplication problem in which each letter
represents a different digit. Can you solve it?
   IF x
  AT
  ---
FIAT


~\cite{clessa1996math}17
How many triangles are there in this figure? 17

Suppose you are visiting an island with knights who always tell the truth, knaves who always lie, and jokers who can do either.

I am a knave?

What must the islander depicted above be?
Joker

You meet three islanders named Ellis, Farin, and Gobi. 
They all know what the others are (a knight, knave or joker) and make the following statements:

If exactly one of them is a joker, how many of them are knights?



Since exactly one of them is a joker, and they all accuse different people of being jokers, then the joker is lying. If the joker were telling the truth, then they would claim that they themselves are the joker, which none of these three are doing.

Given each person is accused by another, one of them is correctly accusing the joker of being a joker so is telling the truth. For instance, suppose that Ellis is the Joker, then Gobi is telling the truth. Or you can suppose that Farin is the joker, in which case Ellis is telling the truth.

This person telling the truth can't be a joker (since as already pointed out, the joker is lying) so the truth-teller must be a knight.

We've concluded that one person is a joker, and at least one is a knight. The third person can't be a knight (they must be a knave), because the knight and the third person are saying that different people are jokers, which is impossible with only one joker. For instance, if Ellis is the joker, then Gobi is telling the truth (and is a knight), and Farin is lying (and is a knave).

So, since there is only one truth-teller there must be only one knight.

Note: "None of them are knights" is incorrect because one of them is a joker, and all of them point to another person as the joker. One of them has to be telling the truth, and it's not the joker.


%%%%%%%%
There are 3 boxes, exactly one of which has a car. You can keep the car if you pick the correct box!

On each box there is a statement, exactly one of which is true.

Box 1: The car is in this box.
Box 2: The car is not in this box.
Box 3: The car is not in box 1.

Which box has the car?
Explanation

Correct answer: Box 2

If Box 2 contains the car, then the statement on Box 2 would be False (it is in box 2!), the statement on Box 1 would be False (it's not in box 1), and only the statement on Box 3 is True (yes, the car is not in box 1). Thus, it looks like the car is in Box 2!

But, let's rule out the other possibilities to double check!

If Box 1 contains the car, then the statements on both Box 1 and Box 2 are true, so this is impossible.
If Box 3 contains the car, then the statements on both Box 2 and Box 3 are true, so this is impossible.




You have four closed boxes as shown:

While you know all four types of food are inside and each box only contains one type of food, you also know that only one of the boxes is labeled correctly. What's the minimum number of boxes that you need to open to be guaranteed to find out which one is labeled correctly? (Note: Guaranteed means in all possible scenarios, so you can't assume one that is lucky.)
Explanation

Correct answer: 2

Open the box labeled Apples; if it's labeled correctly we're done (though that's just luck!), otherwise we'll find either bananas, carrots, or dates. In any of these cases, we know either that the boxes labeled Bananas, Carrots, or Dates must also be mislabeled.

(Note that this eliminates two boxes at once! For example, if you find dates in the Apples box, then both Apples and Dates are wrong.)

If the first opened box has bananas inside, then the box labeled Bananas is incorrect and either Carrots or Dates are correct.
If the first opened box has carrots inside, then the box labeled Carrots is incorrect and either Bananas or Dates are correct.
If the first opened box has dates inside, then the box labeled Dates is incorrect and either Bananas or Carrots are correct.

No matter the circumstance, after opening one box we're down to two remaining boxes that might be the correctly labeled box. Open either one of them. If it's the correctly labeled box, we've found it. Otherwise the remaining unopened box is correctly labeled and we've found it. We don't need to open it to double check.


*********************************
Truth-Seeking

In front of you are 3 chests, labeled as shown:

You are told that all of the labels are incorrectly placed. Each label describes the contents of a different chest. To determine which chest contains 100 gold coins, you are allowed to pick a single random coin from a chest of your choice.

Which chest should you pick a coin from?

Note: The picking of a single coin is just a sample to figure out where the 100 gold coins are. The single coin is random, you don't get to look inside. Plus the chest you choose to pick the coin from does not, necessarily, need to be the chest of 100 gold coins. You're picking a chest first to determine which chest it is that has 100 gold coins in it.
Explanation

Correct answer: Chest B

First, note that since all the chests are mislabeled, we already know some facts about the chests:

    A must have either 50 gold/50 silver or 100 silver.
    B must have either 100 gold or 100 silver.
    C must have either 50 gold/50 silver or 100 gold.

Suppose you pick a coin from chest A:

    If the coin is gold, we've eliminated "100 silver coins" as a possibility for chest A, leaving 50 gold/50 silver, meaning C must have the 100 gold, and B is 100 silver. However, there is no guarantee that we would pull a gold coin from a 50 gold/50 silver chest. We want our choice of chest that we pick a coin from to work even in the worst case scenario.
    If the coin is silver, no new information is learned: Chest A could still be either 50 gold & 50 silver or 100 silver. We have not eliminated either option.

Suppose you pick a coin from chest C:

    If the coin is gold, no new information is learned: the chest is either 50 gold & 50 silver or 100 gold. We have not eliminated either option.
    If the coin is silver, we've eliminated "100 gold" as a possibility for chest C, and the gold coins must be in chest B, leaving A with 100 silver. However, we are only drawing a single coin from a chest that is split 50-50; we're not guaranteed a pick of silver, so we can't depend on this happening!

Suppose you pick a coin from chest B:

    If the coin is gold, we've eliminated "100 silver coins" as a possibility for chest B, and the 100 gold must be in chest B.
    If the coin is silver, we've eliminated "100 gold coins" as a possibility for chest B, and the 100 gold must be in chest C.

If you pick from chest B, picking either gold or silver will let us know where the 100 gold coins are, without depending on any luck while picking from a chest that is split 50-50, so that is the correct chest to pick.

~\cite{clessa1996math}
Write down the next number in this series:
18,46,94,63,52, ?
 Cum se pot rezolva astfel de probleme?
 
 24 in ~\cite{clessa1996math} Practice arithmetic in mace4
 
 There's a three digit number which:
if you add seven to it it divides exactly by seven;
if you add eight to it it divides exactly by eight;
if you add nine to it it divides exactly by nine.

What is the number?

 44 in ~\cite{clessa1996math} Practice arithmetic in mace4
  A simple number crossword.
A
B
c
Across Down
(A) A square.
(C) Al3. (A) 8 down - C across + 22.
(8) Multiple of 13.

48~\cite{clessa1996math} Another simple number crossword.
A
B
c
Across
Down
(A) A down -15 (and a multiple of 17). (A) A square.
(C) A beastly number.
(B) A square +2.

How many two-digit positive whole numbers are there?


59. Find four consecutive prime numbers that add up to 220.


~\cite{clessa1996math}
micropuzzle 58 a number crossword

~\cite{clessa1996math}
micropuzzle 59 a number crossword

~\cite{clessa1996math}
65 the cocktail party.

https://l4f.cecs.anu.edu.au/